\vspace*{1.6cm}
\noindent
{\xiaosibf
Our aim is to provide customers with timely and comprehensive service. For any\\
assistance, please contact our company headquarters:}

\vspace{\baselineskip}
\noindent
{\xiaosibf
Quectel Wireless Solutions Co., Ltd.}\\
Office 501, Building 13, No.99, Tianzhou Road, Shanghai, China, 200233\\
Tel: +86 21 5108 6236\\
Email: \underline{info@quectel.com}\\

\vspace{\baselineskip}
\noindent
{\xiaosibf
Or our local office. For more information, please visit:}\\
\underline{http://www.quectel.com/support/salesupport.aspx}\\

\vspace{\baselineskip}
\noindent
{\xiaosibf
For technical support, or to report documentation errors, please visit:}\\
\underline{http://www.quectel.com/support/techsupport.aspx}\\
Or Email to: \underline{Support@quectel.com}

\vspace{\baselineskip}
\noindent
{\xiaosibf
GENERAL NOTES}\\
QUECTEL OFFERS THE INFORMATION AS A SERVICE TO ITS CUSTOMERS. THE INFORMATION\\
PROVIDED IS BASED UPON CUSTOMERS’ REQUIREMENTS. QUECTEL MAKES EVERY EFFORT\\
TO ENSURE THE QUALITY OF THE INFORMATION IT MAKES AVAILABLE. QUECTEL DOES NOT\\
MAKE ANY WARRANTY AS TO THE INFORMATION CONTAINED HEREIN, AND DOES NOT ACCEPT\\
ANY LIABILITY FOR ANY INJURY, LOSS OR DAMAGE OF ANY KIND INCURRED BY USE OF OR\\
RELIANCE UPON THE INFORMATION. ALL INFORMATION SUPPLIED HEREIN IS SUBJECT TO\\
CHANGE WITHOUT PRIOR NOTICE.

\vspace{\baselineskip}
\noindent
{\xiaosibf
COPYRIGHT}\\
THE INFORMATION CONTAINED HERE IS PROPRIETARY TECHNICAL INFORMATION OF\\
QUECTEL CO., LTD. TRANSMITTING, REPRODUCTION, DISSEMINATION AND EDITING OF THIS\\
DOCUMENT AS WELL AS UTILIZATION OF THE CONTENT ARE FORBIDDEN WITHOUT\\
PERMISSION. OFFENDERS WILL BE HELD LIABLE FOR PAYMENT OF DAMAGES. ALL RIGHTS\\
ARE RESERVED IN THE EVENT OF A PATENT GRANT OR REGISTRATION OF A UTILITY MODEL\\
OR DESIGN.

\vspace{\baselineskip}
\vspace{\baselineskip}
\noindent
{\xiaosibf
\emph{Copyright © Quectel Wireless Solutions Co., Ltd. 2017. All rights reserved.}}
\clearpage
